---
title: "Alcohol vs Seat choice"
author: "Christopher Mojarro"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The visual in the back plot shows a large difference the back row and the
middle row. The plot also shows an even larger difference between the back and 
front row.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

According to the chart the back row drinks 8.555556 more drinks than the 
middle row, drinking only 3.3 drinks per week. The front row drinks 1.7 per week.
It is to assume that they aren't all drinking the same amount. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The P value represents the chances of getting a result as we just obtained if the 
null hypothesis is true. Since the result is so small I reject the null hypothesis.

We follow to discover the difference.

```{r}
plot(TukeyHSD(model1))
```


According to the chart the middle and front row are not different. Although
the front-back and the back middle are different

## Conclusions


